Preprocessing Real-World Data

### 2022-12-23 intro.qmd
merry xmas

plt_original = plot(mod, counterfactual_data; zoom=0, colorbar=false, title="(a)")
```

@@

candidates = findall(ys.==0)
chosen_individuals = rand(candidates, Int(round(μ*length(candidates))))
X′ = copy(X)
y′ = copy(ys)
factuals = select_factual(counterfactual_data,chosen_individuals)
outcome = generate_counterfactual(factuals, 1, counterfactual_data, mod, gen; initialization=:identity)
X′[:,chosen_individuals] = reduce(hcat, @.(selectdim(counterfactual(outcome), 3, 1)))
y′[chosen_individuals] = reduce(vcat,@.(selectdim(counterfactual_label(outcome),3,1)))
counterfactual_data′ = CounterfactualData(X′,y′')
plt_single = plot(mod,counterfactual_data′;zoom=0,colorbar=false,title="(b)")
```

@@

mod = Models.train(mod, counterfactual_data′)
plt_single_retrained = plot(mod,counterfactual_data′;zoom=0,colorbar=false,title="(c)")
```

@@

plt = plot(plt_original, plt_single, plt_single_retrained, plt_single_repeat, layout=(1,4), legend=false, axis=nothing, size=(600,165))
savefig(plt, joinpath(www_path, "poc.png"))
plt
```

>>>>

plt_original = plot(mod, counterfactual_data; zoom=0, colorbar=false, title="(a)")
display(plt_original)
```

@@

candidates = findall(ys.==0)
chosen_individuals = rand(candidates, Int(round(μ*length(candidates))))
X′ = copy(X)
y′ = copy(ys)
factuals = select_factual(counterfactual_data,chosen_individuals)
outcome = generate_counterfactual(factuals, 1, counterfactual_data, mod, gen; initialization=:identity)
X′[:,chosen_individuals] = reduce(hcat, @.(selectdim(counterfactual(outcome), 3, 1)))
y′[chosen_individuals] = reduce(vcat,@.(selectdim(counterfactual_label(outcome),3,1)))
counterfactual_data′ = CounterfactualData(X′,y′')
plt_single = plot(mod,counterfactual_data′;zoom=0,colorbar=false,title="(b)")
display(plt_single)
```

@@

mod = Models.train(mod, counterfactual_data′)
plt_single_retrained = plot(mod,counterfactual_data′;zoom=0,colorbar=false,title="(c)")
display(plt_single_retrained)
```

@@

plt = plot(plt_original, plt_single, plt_single_retrained, plt_single_repeat, layout=(1,4), legend=false, axis=nothing, size=(600,165))
savefig(plt, joinpath(www_path, "poc.png"))
display(plt)
```

### 2022-12-23 sections/data_preprocessing/_real_world_data.qmd
rejigged artifacts
merry xmas

---
title: Preprocessing Real-World Data
---

@@

## California Housing Data

@@

@@

@@

## Give Me Some Credit

@@

## UCI Credit Card Default

@@

```{julia}
transformer = Standardizer(count=true) |> ContinuousEncoder()
mach = MLJBase.fit!(machine(transformer, df_balanced[:,Not(:target)]))
X = MLJBase.transform(mach, df_balanced[:,Not(:target)])
schema(X)
```

@@

>>>>

## Preprocessing Real-World Data

@@

### California Housing Data

@@

```{julia}
#| output: true

schema(df_balanced)
```

@@

```{julia}
#| output: true

transformer = Standardizer(count=true)
mach = MLJBase.fit!(machine(transformer, df_balanced[:,Not(:target)]))
X = MLJBase.transform(mach, df_balanced[:,Not(:target)])
schema(X)
```

@@

### Give Me Some Credit

@@

### UCI Credit Card Default

@@

```{julia}
#| output: true

transformer = Standardizer(count=true) |> ContinuousEncoder()
mach = MLJBase.fit!(machine(transformer, df_balanced[:,Not(:target)]))
X = MLJBase.transform(mach, df_balanced[:,Not(:target)])
schema(X)
```

@@

```{julia}
generate_artifacts(data_path)
```
